The perceptual dimensions of \\ sonority-driven epenthesis

### 2013-10-01 paper.tex
Resolved some formatting issues with brackets

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[table]{xcolor}    %for shading*
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{mathpazo}
\usepackage{tipa}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{linguex}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usepackage{slashbox}	
\usepackage{pifont}    %for pointing hand
\usepackage{arydshln}  %for dashed lines
\usepackage{rotating}  %for angled text
\usepackage{wasysym}   %for frowny face
\usepackage{amssymb} % for angle symbol

\usepackage{amsfonts}
\newcommand{\tickYes}{\checkmark}
\usepackage{pifont}
\newcommand{\tickNo}{\hspace{1pt}\ding{55}}

@@

\ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
     \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
         Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n & $\mathcal{M}$ \\[0.5ex]
\hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
\hline b. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $<$n & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
      \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
\hline d. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
     \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
         {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $<$n  & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ n \\
         Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}-C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\

@@

  \ex. \label{idiolects} The four idiolects: \citep[(43)]{rose.2000}
       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \b. \label{idiolectb} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \c. \label{idiolectc} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.89254688119*8, 1) {RN};
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {bF};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.5 * 8,2) {};
  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
\end{tikzpicture}
}

@@

Proceeding to idiolect \ref{idiolectb}, we find that [r]-sonorant clusters are allowed word-finally. Because {\sc Sonority Angle} permits a linear separation of the [r]-sonorant clusters from the remainder of the falling sonority clusters, this is straightforward to explain
by the movement of the cut-off line from 1.5 to 1.9.

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {bF};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
\end{tikzpicture}
}

@@

{\sc Sonority Rise} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other, it is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}. This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also, but FT never does.

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
\end{tikzpicture}
}

@@

Rose's approach thus requires the formulation of two constraints specifically targeting [r]. The advantage of doing so is that it avoids the difficulty of forbidding [\textipa{Bm}] clusters which we encountered above. On the other hand, the sonority contour faithfulness approach can get away without specifically mentioning [r] at all, by virtue of the ability of the {\sc Sonority Angle} hierarchy to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.

@@

As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning between idiolects. We begin with data from the main idiolect discussed in Section 4.3 of \citep{rose.2000}.

@@

Triconsonantal clusters must be broken up via epenthesis, indicating that {\sc *CCC} $\gg$ {\sc Dep}. If epenthesis occurs either between C\textsubscript{1}C\textsubscript{2} or between C\textsubscript{2}-C\textsubscript{3}, {\sc *CCC} will be satisfied. We do not need a separate constraint to prevent double epenthesis occurring to produce *[C\textipa{1}C\textipa{1}C].

@@

This holds for all the idiolects. Within each idiolect, we need only explain the location of epenthesis.

There are four idiolects to be explained:

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[table]{xcolor}    %for shading*
\usepackage{fullpage}
\usepackage{natbib}
\usepackage{mathpazo}
\usepackage{tipa}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{linguex}
\usepackage{tikz}
\usetikzlibrary{matrix,arrows}
\usepackage{tkz-euclide}
\usetkzobj{all}
\usepackage{slashbox}	
\usepackage{pifont}    %for pointing hand
\usepackage{arydshln}  %for dashed lines
\usepackage{rotating}  %for angled text
\usepackage{wasysym}   %for frowny face
\usepackage{amssymb} % for angle symbol
\usepackage{longtable}
\usepackage{amsfonts}
\newcommand{\tickYes}{\checkmark}
\usepackage{pifont}
\newcommand{\tickNo}{\hspace{1pt}\ding{55}}

@@

\ex. {\sc Ident(Son$\measuredangle$)}$<$n $\gg$ $\mathcal{M}$
     \a. Scenario 1: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
         Since neither violates {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n & $\mathcal{M}$ \\[0.5ex]
\hline \hline a. & \ding{43} & C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $<$n & \\
\hline b. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $<$n & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
      \b. Scenario 2: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$>$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$<$n \\
          C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} harmonically bound by C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} candidate.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline c. & \ding{43} &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3}  & $<$n & \cellcolor{lightgray} \\
\hline d. & & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$! & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
     \c. Scenario 3: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2})$<$n, {\sc SonAngle}(C\textsubscript{2},C\textsubscript{3})$>$n \\
         {\sc Ident(Son$\measuredangle$)}$<$n determines output, overruling $\mathcal{M}$.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline e. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$!  & \cellcolor{lightgray} \\
\hline f. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3}& $<$n  & \cellcolor{lightgray}$\ast$ \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}
     \d. Scenario 4: {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}), {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ n \\
         Since both candidates violate {\sc Ident(Son$\measuredangle$)}$<$n, $\mathcal{M}$ determines output.
\begin{center} \renewcommand*\arraystretch{1.2}
\scalebox{1}[1]{\begin{tabular}[t]{|rrl||c|c|} \hline 
\multicolumn{3}{|c||}{Input:~/C\textsubscript{1}C\textsubscript{2}C\textsubscript{3}/} & {\sc Ident(Son$\measuredangle$)}$<$n &$ \mathcal{M}$  \\[0.5ex]
\hline \hline g. & &  C\textsubscript{1}C\textsubscript{2}\textipa{@}C\textsubscript{3} & $>$n $\ast$  & \\
\hline h. & \ding{43} & C\textsubscript{1}\textipa{@}C\textsubscript{2}C\textsubscript{3} & $>$n $\ast$ & $\ast$! \\
\hline \end{tabular}} \renewcommand*\arraystretch{1} \end{center}

@@

\ex. Scenario: {\sc SonAngle}(C\textsubscript{2}C\textsubscript{3}) $>$ {\sc SonAngle}(C\textsubscript{1}C\textsubscript{2}) $>$ n \\

@@

  \ex. \label{idiolects} The four idiolects: \citep[(43)]{rose.2000}
       \a. \label{idiolecta} \tickYes OVO, \tickNo rVN \citep{leslau.1964} \newline % \textsc{SonSeq} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{*R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \b. \label{idiolectb} \tickYes OVO, \tickYes rVN \newline %\label{idiolectc} \textsc{SonSeq, *R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1t1f}], [\textipa{s1g1d}]
       \c. \label{idiolectc} \tickNo OVO, \tickNo rVN \newline %\label{idiolectb} \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq, *R-Son} \newline
           [\textipa{k1rm}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]
       \d. \label{idiolectd} \tickNo OVO, \tickYes rVN \newline %\label{idiolectd} \textsc{*R-Son} $\gg$ \textsc{SyllCon} $\gg$ \textsc{Dep-IO} $\gg$ \textsc{SonSeq} \newline
           [\textipa{k1r1m}], [\textipa{s1B1r}], [\textipa{k1ft}], [\textipa{k1tf}], [\textipa{s1gd}]

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.89254688119*8, 1) {RN};
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.5 * 8,2) {};
  \node (dividinglineend)   at (1.5 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.5*8, -0.5) {1.5};
\end{tikzpicture}
}

@@

Proceeding to idiolect \ref{idiolectb}, we find that [r]-sonorant clusters are allowed to undergo epenthesis word-finally. Because {\sc Sonority Angle} permits a linear separation of the [r]-sonorant clusters from the remainder of the falling sonority clusters, this is straightforward to explain
by the movement of the cut-off line from 1.5 to 1.9.

@@

	\node (TR) at (0.124354994547*8, 1) {TR};
	\node (Tb) at (0.183110817262*8, 0.5) {T\textipa{B}};
	\node (FR) at (0.218668945874*8, 1) {FR};
	\node (TN) at (0.266252049151*8, 1.5) {TN};
	\node (Fb) at (0.343023940421*8, 1) {F\textipa{B}};
	\node (NR) at (0.463647609001*8, 1) {NR};
	\node (FN) at (0.540419500271*8, 0.5) {FN};
	\node (TF) at (0.588002603548*8, 1) {TF};
	\node (bR) at (0.726642340682*8, 0.5) {\textipa{B}R};
	\node (Nb) at (0.785398163397*8, 1) {N\textipa{B}};
	\node (RR) at (1.10714871779*8, 1) {RR};
	\node (bb) at (1.19028994968*8, 0.5) {\textipa{BB}};
	\node (NN) at (1.2490457724*8, 1) {NN};
	\node (FF) at (1.32581766367*8, 1.5) {FF};
	\node (TT) at (1.37340076695*8, 1) {TT};
	\node (Rb) at (1.57079632679*8, 1) {R\textipa{B}};
	\node (bN) at (1.65393755868*8, 0.5) {\textipa{B}N};
	\node (RN) at (1.84*8, 1) {RN}; %1.89254688119
	\node (NF) at (2.0344439358*8, 1) {NF};
%	\node (GF) at (2.0344439358*8, 1.5) {GF};
	\node (FT) at (2.11121582707*8, 0.5) {FT};
	\node (bF) at (2.17308367293*8, 1) {\textipa{B}F};
	\node (RF) at (2.21429743559*8, 1.5) {RF};
	\node (RT) at (2.35619449019*8, 1) {RT};
	\node (NT) at (2.35619449019*8, 0.5) {NT};
	\node (bT) at (2.38057989937*8, 1.5) {\textipa{B}T};
  \node (rising) at (0.3*8,2.3) {\underline{Rising sonority}};
  \node (level) at (1.2*8,2.3) {\underline{Level sonority}};
  \node (falling) at (2.2*8,2.3) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,0) {};
  \node (axisend)   at (2.7*8,0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, 0.2) -- (0.0*8, -0.2) -- cycle;
  \draw (1.0*8, 0.2) -- (1.0*8, -0.2) -- cycle;
  \draw (2.0*8, 0.2) -- (2.0*8, -0.2) -- cycle;
  \node (0pointlabel) at (0.0,-0.5) {0};
  \node (1pointlabel) at (1.0*8,-0.5) {1};
  \node (2pointlabel) at (2.0*8,-0.5) {2};
  \node (xaxislabel) at (2.7*8,-0.5) {\textsc{SonAngle}};
  % dividing line
  \node (dividinglinestart) at (1.9 * 8,2) {};
  \node (dividinglineend)   at (1.9 * 8,-0.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
  \node (dividingpointlabel) at (1.9*8, -0.5) {1.9};
  \path [line,dotted] (1.5 * 8,1.8) -- (1.91 * 8, 1.8);
\end{tikzpicture}
}

@@

{\sc Sonority Rise} \citep{flemming.2008} can explain idiolects \ref{idiolecta} and \ref{idiolectc}, where the cut-off is drawn between rising and level sonority clusters on the one hand and falling sonority clusters on the other. It is less straightforward to explain the behaviour of idiolects \ref{idiolectb} and \ref{idiolectd}. This is because the cluster hierarchy predicted by {\sc Sonority Rise} does not permit a linear separation of [r]-sonorant clusters from the other falling sonority clusters: if RN undergoes epenthesis, we expect that FT and NF should also do so, but FT never does.

\ex. TODO

\bigskip
\resizebox{\linewidth}{!}{
\begin{tikzpicture}[scale=0.8,shorten >=1pt,->]
  \tikzstyle{line} = [draw, -latex']
  \node (RT) at (2.5*8, 0)  {RT};
  \node (NT) at (1.67*8,0)  {NT};
  \node (FT) at (1.25*8,0)  {FT};
  \node (TT) at (1*8,-0.5)     {TT};
  \node (RF) at (2*8,0)     {RF};
  \node (NF) at (1.33*8,-0.5)  {NF};
  \node (FF) at (1*8,0)   {FF};
  \node (TF) at (0.8*8,-0.5)   {TF};
  \node[draw,circle,dashed] (RN) at (1.5*8,0)   {RN};
  \node (NN) at (1*8,0.5)     {NN};
  \node (FN) at (0.75*8,0)  {FN};
  \node (TN) at (0.6*8,0)   {TN};
  \node (RR) at (1*8,1.0)  {RR};
  \node (NR) at (0.67*8,-0.5)  {NR};
  \node (FR) at (0.5*8,0)   {FR};
  \node (TR) at (0.4*8,0)   {TR};
  \node (rising) at (0.5*8,2) {\underline{Rising sonority}};
  \node (level) at (1*8,2) {\underline{Level sonority}};
  \node (falling) at (1.67*8,2) {\underline{Falling sonority}};
  % axis
  \node (axisstart) at (-0.23,-1.0) {};
  \node (axisend)   at (2.7*8,-1.0) {};
  \draw (axisstart) -- (axisend);
  \draw (0.0*8, -1.2) -- (0.0*8, -0.8) -- cycle;
  \draw (1.0*8, -1.2) -- (1.0*8, -0.8) -- cycle;
  \draw (2.0*8, -1.2) -- (2.0*8, -0.8) -- cycle;
  \node (0pointlabel) at (0.0,-1.5) {0};
  \node (1pointlabel) at (1.0*8,-1.5) {1};
  \node (2pointlabel) at (2.0*8,-1.5) {2};
  \node (xaxislabel) at (2.7*8,-1.5) {\textsc{SonRise}};
  % dividing line
  \node (dividinglinestart) at (1.15 * 8,1.5) {};
  \node (dividinglineend)   at (1.15 * 8,-1.3) {};
  \path [line,dashed] (dividinglinestart) -- (dividinglineend) -- cycle;
\end{tikzpicture}
}

@@

Rose's approach thus requires the formulation of two constraints specifically targeting [r]. The advantage of doing so is that it avoids the difficulty of forbidding [\textipa{Bm}] clusters which we encountered above. On the other hand, the sonority contour faithfulness approach does not have to single out [r] for special treatment at all, by virtue of the ability of the {\sc Sonority Angle} hierarchy to group [r]-sonorant clusters together with the level and rising sonority clusters, at the expense of requiring a constraint against [\textipa{Bm}] clusters.

@@

As with coda clusters, there is considerable inter- and intra-speaker variability in epenthetic positioning.

@@

Triconsonantal clusters must be broken up via epenthesis, indicating that {\sc *CCC} $\gg$ {\sc Dep}. If epenthesis occurs either between C\textsubscript{1}C\textsubscript{2} or between C\textsubscript{2}C\textsubscript{3}, {\sc *CCC} will be satisfied. We do not need a separate constraint to prevent double epenthesis occurring to produce *[C\textipa{1}C\textipa{1}C].

\ex. TODO

@@

This holds for all the ``idiolects'' reported in \citep{rose.2000}. Within each, we need only explain the location of epenthesis.

There are four idiolects to be explained. Note that these do not appear to correlate systematically with the four coda cluster idiolects.
